|

### 2023-02-06 paper_comparison/paper_comparison/paper_comparison.Rmd
use "data collection period" to replace "experiment"

Three experiments are conducted to investigate the difference between conventional hypothesis testing and visual inference in the application of linear regression diagnostics. Two types of departures, namely non-linearity and heteroskedasticity, are considered with the corresponding data generating process being designed for experiment I and II. The experiment III is designed for collecting human responses to null lineups such that the parameter $\alpha$ in Equation \ref{eq:pvalue-beta-binomial} can be estimated. Overall, we plan to collect `r vi_survey  %>% filter(!attention_check) %>% nrow()` evaluations on `r vi_survey  %>% filter(!attention_check) %>% pull(unique_lineup_id) %>% unique() %>% length()` unique lineups performed by `r vi_survey  %>% filter(!attention_check) %>% count(exp, set) %>% nrow()` subjects throughout three experiments.

@@

Experiment I is designed to study the ability of human subjects to detect the effect of a non-linear term $\boldsymbol{z}$ constructed using Hermite polynomials on random vector $\boldsymbol{x}$ formulated as

@@

```{r results='asis'}
data.frame(j = c("2", "3", "6", "18", ""),
           sigma = c("0.25", "1.00", "2.00", "4.00", ""),
           a = c("-1", "0", "1", "", ""),
           b = c("0.25", "1.00", "4.00", "16.00", "64.00"),
           n = c("50", "100", "300", "", ""), 
           x_dist = c("Uniform", "Normal", "Skewed", "Discrete uniform", "")) %>%
  knitr::kable(col.names = NULL,
               align = "rr|rr|rc",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Levels of the factors used in experiments I, II, III.', 
               label = "model-factor-table" ) %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  kableExtra::add_header_above(c("Poly Order (sym1)", #"Order of Hermite polynomial\n(sym1)", 
                                 "SD (sym3)", #"Standard deviation of polynomial model\n(sym3)",
                                 "Shape (sym4)", # "Shape of heteroskedasticity\n(sym4)", 
                                 "Ratio (sym5)", # Variance factor of heteroskedasticity model\n(sym5)",
                                 "Size (sym6)", 
                                 "Distribution of fitted values")) %>% #"Sample size\n(sym6)")) %>%
  kableExtra::add_header_above(c("Non-linearity" = 2, 
                               "Heteroskedasticity" = 2, "Common" = 2)) %>%
  as.character() %>%
  gsub("sym1", "$j$", .) %>%
  gsub("sym3", "$\\\\sigma$", .) %>%
  gsub("sym4", "$a$", .) %>%
  gsub("sym5", "$b$", .) %>%
  gsub("sym6", "$n$", .) %>%
  cat()
```

```{r different-shape-of-herimite, fig.height = 2, fig.cap = "Polynomial forms generated for the residual plots used in experiment I. The four shapes are generated by varying the order of polynomial given by $j$ in $He_j(.)$."}

@@

Figure \ref{fig:example-poly-lineup} demonstrates one of the lineups used in experiment I. This lineup is produced by the non-linearity model with $j = 6$ and uniform fitted values. The data plot location is $2^3 - 4$. All five subjects correctly identify the data plot from this lineup.

```{r different-n, fig.height = 2.67, fig.cap = "Number of observations $n$ have an impact on the strength of the signal. Three different values of $n$ are used in experiment I, II and III."}

@@

```{r different-sigma, fig.height = 2, fig.cap = "For the non-lienearity model, the standard deviation of the error term $\\sigma$ affects the strength of the signal. Four different values of $\\sigma$ are used in the experiment I."}

@@

```{r example-poly-lineup, fig.height = 7, fig.width = 7, fig.cap = "One of the lineups containing non-linearity patterns used in experiment I. Can you spot the most different plot? The data plot is positioned at $2^3 + 1$."}
VI_MODEL$plot_lineup(vi_lineup$poly_24$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

Experiment II is designed to study the ability of human subjects to detect the appearance of a heteroskedasticity pattern under a simple linear regression model setting:

@@

```{r different-shape-of-heter, fig.height = 2.67, fig.cap = "Heteroskedasticity forms used in experiment II. Three different shapes (a = -1, 0, 1) are used in the experiment to create left-triangle, butterfly and right-triangle shapes."}

@@

```{r different-b, fig.height = 2, fig.cap = "Five different values of $b$ are used in experiment II to control the strength of the signal."}

@@

```{r example-heter-lineup, fig.height = 7, fig.width = 7, fig.cap = "One of the lineups containing heteroskedasticity pattern used in experiment II. Can you spot the most different plot? The data plot is positioned at $3^3 - 3^2$"}

@@

An example lineup of this model used in Experiment II is shown in Figure \ref{fig:example-heter-lineup} with $a = -1$ and $X_{raw} \sim U(-1, 1)$. The data plot location is $2^4 + 2$. Nine out of 11 subjects correctly identify the data plot from this lineup.

### Factors common to both experiments

@@

As summarised in Table \ref{tab:model-factor-table}, three additional parameters $n$, $\sigma$ and $b$ are used to control the strength of the signal so that different difficulty levels of lineups are generated, and therefore, the estimated power curve will be smooth and continuous. Parameter $\sigma \in \{0.5, 1, 2, 4\}$ and $b \in \{0.25, 1, 4, 16, 64\}$ are used in experiment I and II respectively. Figure \ref{fig:different-sigma} and \ref{fig:different-b} demonstrate the impact of these two parameters. A large value of $\sigma$ will increase the variation of the error of the non-linearity model and decrease the visibility of the visual pattern. The parameter $b$ controls the standard deviation of the error across the support of the regressor. Given $x \neq a$, a larger value of $b$ will lead to a larger ratio of the variance at $x$ to the variance at $x - a = 0$, making the visual pattern more obvious.

Three different sample sizes are used (n = 50, 100, 300) in all three experiments. It can be observed from Figure \ref{fig:different-n} that with fewer data points drawn in a residual plot, the visual pattern is more difficult to be detected.

@@

Three replications are made for each of the parameter values shown in Table \ref{tab:model-factor-table} resulting in $(4 \times 4 \times 4 \times 3 + 4 \times 3 \times 5 \times 3) \times 3 = `r (4 * 4 * 4 * 3 + 4 * 3 * 5 * 3) * 3`$ different lineups. In addition, each lineup is designed to be evaluated by five different subjects. After attempting some pilot studies internally in our research group, we decide to present a block of 20 lineups to every subject. And to ensure the quality of the survey data, two lineups with obvious visual patterns are included as attention checks. Thus, $576 \times 5 / (20-2) = `r 576 * 5 / 18`$ and $540 \times 5 / (20-2) = `r 540 * 5 / 18`$ subjects are recruited to satisfy the design of the experiment I and experiment II respectively.

As mentioned in Section \ref{calculating-p-values-for-the-visual-test}, $\alpha$ used in Equation \ref{eq:pvalue-beta-binomial} needs to be estimated using null lineups. Hence, three replications of 36 lineups with all combinations of $n$ and fitted value distributions are included in experiment III. In these lineups, the data of the data plot is generated from a model with zero effect size, while the data of the 19 null plots are generated using the same simulation method discussed in Section \ref{sampling-from-the-null-distribution}. This generation procedure differs from the canonical Rorschach lineup procedure, which requires that all 20 plots are generated from the null hypothesis. However, these lineups serve the same fundamental purpose: to assess the number of visually interesting plots generated under the null hypothesis.

@@

All lineups consist of only null plots are planned to be evaluated by 20 subjects. 
However, presenting only these lineups to subjects are considered to be bad practices as subjects will lose interest quickly. 
Therefore, we plan to collect 6 more evaluations on the 279 lineups with uniform fitted values, result in $(36 \times 20 + (4 \times 4 \times 3 + 3 \times 5 \times 3) \times 3 \times 6) / (20-2) = `r (36 * 20 + (4 * 4 * 3 + 3 * 5 * 3) * 3 * 6) / 18`$ subjects recruited for experiment III.

@@

Subjects for all three experiments are recruited from an crowdsourcing platform called Prolific [@palan2018prolific]. Prescreening procedure is applied during the recruitment, subjects are required to be fluent in English, with $98\%$ minimum approval rate and 10 minimum submissions in other studies.

@@

In every lineup evaluation, the subject is asked to select one or more plots that are most different from others, provide a reason for their selections, and evaluate how different they think the selected plots are from others. If there is no noticeable difference between plots in a lineup, subjects are permitted to select zero plots without providing the reason. No subject are shown the same lineup twice. Information about preferred pronoun, age group, education, and previous experience in visual experiment are also collected. A subject's submission is only accepted if the data plot is identified for at least one attention check. Data of rejected submissions are discarded automatically to maintain the overall data quality.

@@

There are `r 160 * 18`, `r 150 * 18` and `r 133 * 18 - nrow(filter(vi_survey, null_lineup, !attention_check))` lineups evaluation made by 160, 150 and 133 subjects recruited for experiment I, II and III respectively. In the total of `r nrow(filter(vi_survey, !attention_check))` lineup evaluations, `r nrow(filter(vi_survey, type == "polynomial", !attention_check))` use lineups produced by the non-linearity model, and `r nrow(filter(vi_survey, type == "heteroskedasticity", !attention_check))` use lineups produced by the heteroskedasticity model. Besides, there are `r nrow(filter(vi_survey, attention_check))` attention checks and `r nrow(filter(vi_survey, null_lineup, !attention_check))` evaluations on null lineups needed for the estimate of $\alpha$ not included in the analysis. The collated dataset is provided in `vi_survey` of the `visage` `R` package.

@@

```{r different-x-dist-poly-power, fig.cap = "Comparison of power on lineups with different fitted value distributions, for conventional tests and visual tests. Each power curve of the uniform distribution is surrounded by a grey line to indicate it is the baseline in its group. For both types of tests power does change. The discrete fitted value distribution substantially lowers the power for non-linearity patterns in residual plots. For heteroskedasticity patterns, normal and lognormal distributions produce lower power."}

@@

  # Bold the uniform smooth line
  geom_smooth(data = ~filter(.x, x_dist == "Uniform"),
              aes(log_effect_size, reject), 
              col = "grey", 
              se = FALSE, 
              span = 0.03,
              size = 3) +

  # Draw all smooth lines
  geom_smooth(aes(log_effect_size, reject, col = x_dist), 
              span = 0.03,
              se = FALSE, 
              size = 1) +

@@

This paper has demonstrated that conventional residual-based statistical tests are more sensitive to departures from assumptions for residuals than visual tests evaluated by humans in the diagnostics of linear regression models. Three experiments are conducted with two simulation models designed for non-linearity and heteroskedasticity model defects being applied. Methods for obtaining the $p$-value of visual tests proposed by @vanderplas2021statistical are extended to allowed for multiple selections in a lineup protocol.

@@

Throughout the three human subject experiments we conducted, residual plots rejected by visual tests are rarely not rejected by conventional tests, but departures of residuals that are of little practical sense to humans will often be alarmed by conventional tests, supporting the common guidance given by experts to utilize graphical representations of data in model diagnostics.

We have also found that residual-based conventional tests relying on a user-parameterized test formula, such as the RESET test, will suffer from a decrease in power for detecting certain residual departures intended to be tested but not covered by the test formula. This can not be avoided without prior knowledge of their functional forms, which is usually obtained by plotting the residuals. On the other hand, visual tests do not rely on such information and a collection of departures can be tested simultaneously.

Besides, fitted value distributions

with different

symmetric, evenly

@@

@@

>>>>

1. experiments -> data collection periods

To investigate the difference between conventional hypothesis testing and visual inference in the application of linear regression diagnostics, an experiment is conducted in three data collection periods. Two types of departures, namely non-linearity and heteroskedasticity, are considered with the corresponding data generating process being designed for data collection periods I and II. The data collection period III is designed for collecting human responses to null lineups such that the parameter $\alpha$ in Equation \ref{eq:pvalue-beta-binomial} can be estimated. Overall, we plan to collect `r vi_survey  %>% filter(!attention_check) %>% nrow()` evaluations on `r vi_survey  %>% filter(!attention_check) %>% pull(unique_lineup_id) %>% unique() %>% length()` unique lineups performed by `r vi_survey  %>% filter(!attention_check) %>% count(exp, set) %>% nrow()` subjects throughout three data collection periods.

@@

Data collection period I is designed to study the ability of human subjects to detect the effect of a non-linear term $\boldsymbol{z}$ constructed using Hermite polynomials on random vector $\boldsymbol{x}$ formulated as

@@

```{r results='asis'}
data.frame(j = c("2", "3", "6", "18", ""),
           sigma = c("0.25", "1.00", "2.00", "4.00", ""),
           a = c("-1", "0", "1", "", ""),
           b = c("0.25", "1.00", "4.00", "16.00", "64.00"),
           n = c("50", "100", "300", "", ""), 
           x_dist = c("Uniform", "Normal", "Skewed", "Discrete uniform", "")) %>%
  knitr::kable(col.names = NULL,
               align = "rr|rr|rc",
               escape = FALSE,
               format = "latex",
               booktabs = TRUE, 
               caption  = 'Levels of the factors used in data collection periods I, II, III.', 
               label = "model-factor-table" ) %>%
  kableExtra::kable_styling(latex_options = "scale_down") %>%
  kableExtra::add_header_above(c("Poly Order (sym1)", #"Order of Hermite polynomial\n(sym1)", 
                                 "SD (sym3)", #"Standard deviation of polynomial model\n(sym3)",
                                 "Shape (sym4)", # "Shape of heteroskedasticity\n(sym4)", 
                                 "Ratio (sym5)", # Variance factor of heteroskedasticity model\n(sym5)",
                                 "Size (sym6)", 
                                 "Distribution of fitted values")) %>% #"Sample size\n(sym6)")) %>%
  kableExtra::add_header_above(c("Non-linearity" = 2, 
                               "Heteroskedasticity" = 2, "Common" = 2)) %>%
  as.character() %>%
  gsub("sym1", "$j$", .) %>%
  gsub("sym3", "$\\\\sigma$", .) %>%
  gsub("sym4", "$a$", .) %>%
  gsub("sym5", "$b$", .) %>%
  gsub("sym6", "$n$", .) %>%
  cat()
```

```{r different-shape-of-herimite, fig.height = 2, fig.cap = "Polynomial forms generated for the residual plots used in data collection period I. The four shapes are generated by varying the order of polynomial given by $j$ in $He_j(.)$."}

@@

Figure \ref{fig:example-poly-lineup} demonstrates one of the lineups used in data collection period I. This lineup is produced by the non-linearity model with $j = 6$ and uniform fitted values. The data plot location is $2^3 - 4$. All five subjects correctly identify the data plot from this lineup.

```{r different-n, fig.height = 2.67, fig.cap = "Number of observations $n$ have an impact on the strength of the signal. Three different values of $n$ are used in data collection periods I, II and III."}

@@

```{r different-sigma, fig.height = 2, fig.cap = "For the non-lienearity model, the standard deviation of the error term $\\sigma$ affects the strength of the signal. Four different values of $\\sigma$ are used in the data collection period I."}

@@

```{r example-poly-lineup, fig.height = 7, fig.width = 7, fig.cap = "One of the lineups containing non-linearity patterns used in data collection period I. Can you spot the most different plot? The data plot is positioned at $2^3 + 1$."}
VI_MODEL$plot_lineup(vi_lineup$poly_24$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

Data collection period II is designed to study the ability of human subjects to detect the appearance of a heteroskedasticity pattern under a simple linear regression model setting:

@@

```{r different-shape-of-heter, fig.height = 2.67, fig.cap = "Heteroskedasticity forms used in data collection period II. Three different shapes (a = -1, 0, 1) are used in the experiment to create left-triangle, butterfly and right-triangle shapes."}

@@

```{r different-b, fig.height = 2, fig.cap = "Five different values of $b$ are used in data collection period II to control the strength of the signal."}

@@

```{r example-heter-lineup, fig.height = 7, fig.width = 7, fig.cap = "One of the lineups containing heteroskedasticity pattern used in data collection period II. Can you spot the most different plot? The data plot is positioned at $3^3 - 3^2$"}

@@

An example lineup of this model used in data collection period II is shown in Figure \ref{fig:example-heter-lineup} with $a = -1$ and $X_{raw} \sim U(-1, 1)$. The data plot location is $2^4 + 2$. Nine out of 11 subjects correctly identify the data plot from this lineup.

### Factors common to both data collection periods

@@

As summarised in Table \ref{tab:model-factor-table}, three additional parameters $n$, $\sigma$ and $b$ are used to control the strength of the signal so that different difficulty levels of lineups are generated, and therefore, the estimated power curve will be smooth and continuous. Parameter $\sigma \in \{0.5, 1, 2, 4\}$ and $b \in \{0.25, 1, 4, 16, 64\}$ are used in data collection periods I and II respectively. Figure \ref{fig:different-sigma} and \ref{fig:different-b} demonstrate the impact of these two parameters. A large value of $\sigma$ will increase the variation of the error of the non-linearity model and decrease the visibility of the visual pattern. The parameter $b$ controls the standard deviation of the error across the support of the regressor. Given $x \neq a$, a larger value of $b$ will lead to a larger ratio of the variance at $x$ to the variance at $x - a = 0$, making the visual pattern more obvious.

Three different sample sizes are used (n = 50, 100, 300) in all three data collection periods. It can be observed from Figure \ref{fig:different-n} that with fewer data points drawn in a residual plot, the visual pattern is more difficult to be detected.

@@

Three replications are made for each of the parameter values shown in Table \ref{tab:model-factor-table} resulting in $(4 \times 4 \times 4 \times 3 + 4 \times 3 \times 5 \times 3) \times 3 = `r (4 * 4 * 4 * 3 + 4 * 3 * 5 * 3) * 3`$ different lineups. In addition, each lineup is designed to be evaluated by five different subjects. After attempting some pilot studies internally in our research group, we decide to present a block of 20 lineups to every subject. And to ensure the quality of the survey data, two lineups with obvious visual patterns are included as attention checks. Thus, $576 \times 5 / (20-2) = `r 576 * 5 / 18`$ and $540 \times 5 / (20-2) = `r 540 * 5 / 18`$ subjects are recruited to satisfy the design of the data collection period I and II respectively.

As mentioned in Section \ref{calculating-p-values-for-the-visual-test}, $\alpha$ used in Equation \ref{eq:pvalue-beta-binomial} needs to be estimated using null lineups. Hence, three replications of 36 lineups with all combinations of $n$ and fitted value distributions are included in data collection period III. In these lineups, the data of the data plot is generated from a model with zero effect size, while the data of the 19 null plots are generated using the same simulation method discussed in Section \ref{sampling-from-the-null-distribution}. This generation procedure differs from the canonical Rorschach lineup procedure, which requires that all 20 plots are generated from the null hypothesis. However, these lineups serve the same fundamental purpose: to assess the number of visually interesting plots generated under the null hypothesis.

@@

All lineups consist of only null plots are planned to be evaluated by 20 subjects. 
However, presenting only these lineups to subjects are considered to be bad practices as subjects will lose interest quickly. 
Therefore, we plan to collect 6 more evaluations on the 279 lineups with uniform fitted values, result in $(36 \times 20 + (4 \times 4 \times 3 + 3 \times 5 \times 3) \times 3 \times 6) / (20-2) = `r (36 * 20 + (4 * 4 * 3 + 3 * 5 * 3) * 3 * 6) / 18`$ subjects recruited for data collection period III.

@@

Subjects for all three data collection periods are recruited from an crowdsourcing platform called Prolific [@palan2018prolific]. Prescreening procedure is applied during the recruitment, subjects are required to be fluent in English, with $98\%$ minimum approval rate and 10 minimum submissions in other studies.

@@

In every lineup evaluation, the subject is asked to select one or more plots that are most different from others, provide a reason for their selections, and evaluate how different they think the selected plots are from others. If there is no noticeable difference between plots in a lineup, subjects are permitted to select zero plots without providing the reason. No subject are shown the same lineup twice. Information about preferred pronoun, age group, education, and previous experience in visual experiments are also collected. A subject's submission is only accepted if the data plot is identified for at least one attention check. Data of rejected submissions are discarded automatically to maintain the overall data quality.

@@

There are `r 160 * 18`, `r 150 * 18` and `r 133 * 18 - nrow(filter(vi_survey, null_lineup, !attention_check))` lineups evaluation made by 160, 150 and 133 subjects recruited for data collection periods I, II and III respectively. In the total of `r nrow(filter(vi_survey, !attention_check))` lineup evaluations, `r nrow(filter(vi_survey, type == "polynomial", !attention_check))` use lineups produced by the non-linearity model, and `r nrow(filter(vi_survey, type == "heteroskedasticity", !attention_check))` use lineups produced by the heteroskedasticity model. Besides, there are `r nrow(filter(vi_survey, attention_check))` attention checks and `r nrow(filter(vi_survey, null_lineup, !attention_check))` evaluations on null lineups needed for the estimate of $\alpha$ not included in the analysis. The collated dataset is provided in `vi_survey` of the `visage` `R` package.

@@

```{r}
vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(reject_only_5  = as.numeric(p_value_only_5 < 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject), 
              method = "glm", 
              method.args = list(family = binomial()),
              se = FALSE) +
  geom_smooth(aes(log_effect_size, reject_only_5), 
              method = "glm", 
              method.args = list(family = binomial()),
              col = "red",
              se = FALSE) +
  facet_wrap(~type)
```

```{r different-x-dist-poly-power, fig.cap = "Comparison of power on lineups with different fitted value distributions, for conventional tests and visual tests. Each power curve of the uniform distribution is surrounded by a grey line to indicate it is the baseline in its group. For both types of tests power does change. The discrete fitted value distribution substantially lowers the power of visual tests for non-linearity patterns in residual plots. For heteroskedasticity patterns, normal and lognormal distributions produce lower power for both types of tests."}

@@

  # Bold the uniform smooth line
  # geom_smooth(data = ~filter(.x, x_dist == "Uniform"),
  #             aes(log_effect_size, reject), 
  #             col = "grey", 
  #             se = FALSE, 
  #             span = 0.03,
  #             size = 3) +

  # Draw all smooth lines
  geom_smooth(data = ~filter(.x, x_dist != "Uniform"),
              aes(log_effect_size, reject, col = x_dist), 
              span = 0.03,
              se = FALSE, 
              size = 1) +

  geom_smooth(data = vi_survey %>%
                filter(!null_lineup) %>%
                filter(!attention_check) %>%
                filter(x_dist == "uniform") %>%
                group_by(unique_lineup_id) %>%
                summarise(across(everything(), first)) %>%
                mutate(reject = as.numeric(p_value < 0.05)) %>%
                mutate(reject_only_5  = as.numeric(p_value_only_5 < 0.05)) %>%
                mutate(log_effect_size = log(effect_size)) %>%
                mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
                mutate(conv_or_not = "Visual"),
              aes(log_effect_size, reject_only_5, col = "Uniform"),
              method = "glm",
              method.args = list(family = binomial()),
              se = FALSE
              ) +

@@

This paper has demonstrated that conventional residual-based statistical tests are more sensitive to departures from assumptions for residuals than visual tests evaluated by humans in the diagnostics of linear regression models. An experiment is conducted in three data collection periods with two simulation models designed for non-linearity and heteroskedasticity model defects being applied. Methods for obtaining the $p$-value of visual tests proposed by @vanderplas2021statistical are extended to allowed for multiple selections in a lineup protocol.

@@

Throughout the three data collection periods of the human subject experiment we conducted, residual plots rejected by visual tests are rarely not rejected by conventional tests, but departures of residuals that are of little practical sense to humans will often be alarmed by conventional tests, supporting the common guidance given by experts to utilize graphical representations of data in model diagnostics.

We have also found that residual-based conventional tests relying on a user-parameterized test formula, such as the RESET test, will suffer from a significant decrease in power for detecting certain residual departures intended to be tested but not covered by the test formula. This can not be avoided without prior knowledge of their functional forms, which is usually obtained by plotting the residuals. On the other hand, visual tests do not rely on such information and a collection of departures can be tested simultaneously.

fitted value distribution

orientation of heter shape

<!-- Besides, the power of both tests vary for different fitted value distributions.  -->

<!-- The ideal fitted value distribution for a visual test is the uniform distribution. If this can not be satisfied, a continuous -->

<!-- continuous and symmetric -->

<!-- distributions that are continuous, symmetric, or evenly distributed are also welcomed. -->

<!-- properties that a uniform distribution holds, such as continuous, symmetric, and evenly distributed  -->

<!-- Depending on the underlying residual departures embedded in the residual plot,  -->

<!-- In the two controlled scenarios, the conventional tests favours discrete uniform distribution -->

<!-- fitted value distributions have a strong impact on the  -->

<!-- some residual departures are more difficult to be detected under a skewed fitted value distribution.  -->

<!-- continuous, symmetric and evenly distributed. -->

<!-- with different  -->

<!-- symmetric, evenly  -->

@@

recommend residual vs fitted values
a. measure uncertainty
b. systemically miss some structure

@@

1. put #eval in appendix
2. examine batch effect in appendix
3. compute the power of RESET test with different orders (considering dof) (focus on simple pattern possibly?)
